|

### 2022-12-25 rmd/supporting_info.Rmd
edit: add header to SI

---
title: |
  ![](images/logo.png){width=4in}  
output:
  bookdown::pdf_document2:
    fig_caption: true
    number_sections: true
    latex_engine: xelatex
    toc: true
    includes:
        before_body: title.tex
mainfont: "Times New Roman"
fontsize: 11pt
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = "document_output")
      })
header-includes:
  - \pagenumbering{gobble}
  - \usepackage{amsmath, fancyhdr, caption, booktabs}
  - \setlength{\headheight}{13.6pt}
bibliography: reference.bib
csl: https://www.zotero.org/styles/pnas
---

@@

The monitoring program employed a two-pass sampling method at all sampling sites. In each pass, a combination of electrofishing and cast net (two-pass) was used to effectively catch both benthic and water-column species in a given area. The number of cast-net throws was determined as the sampled area divided by $4.5~\text{m}^2$ (the area covered by a cast net). Thus, this sampling method has a constant sampling effort per unit area across sites.

>>>>

---
output:
  bookdown::pdf_document2:
    fig_caption: true
    number_sections: true
    latex_engine: xelatex
    toc: true
    includes:
        before_body: title.tex
mainfont: "Times New Roman"
fontsize: 11pt
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = "document_output")
      })
header-includes:
  - \usepackage{amsmath, fancyhdr, caption, booktabs}
  - \pagestyle{fancy}
  - \renewcommand{\headrulewidth}{0pt}
  - \fancyhead[L]{\includegraphics[width=5cm]{images/logo.png}}
  - \fancyhead[C]{}
  - \pagenumbering{gobble}
  - \setlength{\headheight}{13.6pt}
bibliography: reference.bib
csl: https://www.zotero.org/styles/pnas
---

@@

The monitoring program employed a two-pass sampling method at all sampling sites. In each pass, a combination of electrofishing and cast net was used to effectively catch both benthic and water-column species in a given area. The number of cast-net throws was determined as the sampled area divided by $4.5~\text{m}^2$ (the area covered by a cast net). Thus, this sampling method has a constant sampling effort per unit area across sites.
